### 2018-05-02 paper/security-discussion.tex
final

Alice and Bob also want to prevent Carol and David to learn that Alice sent a 
message to Bob (as defined in \cref{system-model}).
Alice and Bob construct their \ac{SPOR} route by including devices from the 
global set %Global Device Retinue
, which also includes devices from Carol and David.
If all devices on the route belong to Carol and David, then they can, of course, 
learn that Alice sent a message to Bob.
How well they can do if they do not control the entire route, depends on the 
choice of the encryption scheme \(\Enc*\), used to encrypt the message \(m\) 
(see \cref{sec:file_exchange}).

What makes sense is to choose at least an authenticated encryption 
scheme~\cite{AuthEncryption}.
(We could also choose a deniable encryption scheme~\cite{DeniableEncryption}, 
\eg the one by \textcite{OTPKX} which is both deniable and authenticated and 
provides \ac{DEN-SS}.)
This would give confidentiality (or deniability) and integrity for the message, 
but if the first and the last node belong to Carol and David, they can infer 
that Alice sent a message to Bob.
Note that as our in-package header is designed, each node on the route can infer 
its position on the route \emph{relative to the destination}.
(We discuss how to remedy this below.)
None of the nodes can know if the previous node is the originator or not, unless 
they collude with the previous node.
The last node, however, can know for sure that the next hop is the destination, 
but not who it belongs to.

@@

This means that under the assumption of uniformly random peer sampling, we 
achieve the properties we outlined in \cref{system-model}.
Additionally, since Alice and Bob choose a new key for every file, we have 
forward secrecy between files.
\Eg an adversary who compromises either Alice or Bob cannot determine what Alice 
sent to Bob, unless it is an ongoing transfer.

\subsection{Limitations}%
\label{security-limitations}

@@

\subsection{Future Work}

One thing that we can directly improve is the header.
We see two alternative paths for improving the header.
First, we might be able to adapt the Sphinx~\cite{Sphinx} cryptographic packet 
format to the routing of \(\SPOR\).
Then we could achieve the properties of Sphinx, \eg preventing the last node to 
learn the destination, and enjoy provable security.

The second approach would be to use the technique by \textcite{PPACinPubFS}.
They adapt \(\ANOBE\) in such a way that its ciphertexts decrypt to different 
things for different recipients.
This way we could have one ciphertext encrypted for all the alternative nodes 
--- across layers.
Then the ciphertext would decrypt to different plaintexts for nodes on different 
layers in the route.
This would hide the path length (constant-size ciphertexts by padding) and the 
position of individual nodes.
This approach would probably be the easiest, but would probably not provide all 
the properties from Sphinx (\eg resistance to active tagging attacks).

>>>>

Alice and Bob also want to prevent Carol and David to learn that Alice sent a 
message to Bob (as defined in \cref{system-model}).
Alice and Bob construct their \ac{SPOR} route by including devices from the 
global set %Global Device Retinue
, which also includes devices from Carol and David.
If all devices on the route belong to Carol and David, then they can, of course, 
learn that Alice sent a message to Bob.
How well they can do if they do not control the entire route, depends on the 
choice of the encryption scheme \(\Enc*\), used to encrypt the message \(m\). 
%(see \cref{sec:file_exchange}).

What makes sense is to choose at least an authenticated encryption 
scheme~\cite{AuthEncryption}.
(We could also choose a deniable encryption scheme~\cite{DeniableEncryption}, 
\eg \cite{OTPKX} which is authenticated and provides deniability under
surveillance-state attacks.) %is both deniable and authenticated and  provides \ac{DEN-SS}.)
This would give confidentiality (or deniability) and integrity for the message, 
but if the first and the last node belong to Carol and David, they can infer 
that Alice sent a message to Bob.
Note that as our in-package header is designed, each node on the route can infer 
its position on the route \emph{relative to the destination}.
(We discuss how to remedy this below.)
None of the nodes can know if the previous node is the originator or not, unless 
they collude with the previous node.
The last node, however, can know for sure that the next hop is the destination, 
but not who it belongs to.

@@

This means that under the assumption of uniformly random peer sampling, we 
achieve the properties we outlined in \cref{system-model}.
Additionally, since Alice and Bob choose a new key for every file, we have 
forward secrecy between files.
\Eg an adversary who compromises either Alice or Bob cannot determine what Alice 
sent to Bob, unless it is an ongoing transfer.
\\
%\subsection{Limitations}%
\label{security-limitations}

@@

% \subsection{Future Work}

% One part that we can directly improve is the header.
% We see two alternative paths for improving the header.
% First, we might be able to adapt the Sphinx~\cite{Sphinx} cryptographic packet 
% format to the routing of \(\SPOR\).
% Then we could achieve the properties of Sphinx, \eg preventing the last node to 
% learn the destination, and enjoy provable security.

% The second approach would be to use the technique by \textcite{PPACinPubFS}.
% They adapt \(\ANOBE\) in such a way that its ciphertexts decrypt to different 
% things for different recipients.
% This way we could have one ciphertext encrypted for all the alternative nodes 
% --- across layers.
% Then the ciphertext would decrypt to different plaintexts for nodes on different 
% layers in the route.
% This would hide the path length (constant-size ciphertexts by padding) and the 
% position of individual nodes.
% This approach would probably be the easiest, but would probably not provide all 
% the properties from Sphinx (\eg resistance to active tagging attacks).
